\Large On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory

### 2025-06-24 2nd report/2report.tex
New

    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
    \begin{align*}
    A_5[1^+2^+3^+4^+5^+] &= 0 
    \qquad (\!+,-:~\text{\hyperlink{helicity}{helicity};} \\
    A_5[1^-2^+3^+4^+5^+] &= 0 
    \qquad 1,2,\cdots,n:~\text{particle labels}) \\
    \end{align*}
    \pause
    \vspace{-3em}
    \hypertarget{conv}{}
    \begin{gather*}
    \textcolor{red}{A_5[1^-2^-3^+4^+5^+]= 
    \frac{\langle 1 2 \rangle^4}
         {\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle45 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trivial one})\\[1em]
    (p_{i\mu} \sigma^\mu)_{\alpha\dot{\alpha}}=(\aket{p_i})_\alpha([p_i|)_{\dot{\alpha}},\quad \aket{p_i}=\aket{i}\\
    \quad \sigma^\mu=(1,\vec{\sigma}),\quad \aket{i},\sket{i}: \text{Weyl Spinors}\\
    \avg{ij}=\langle i |^\alpha \aket{j}_\alpha=\varepsilon^{\alpha\beta}\aket{i}_\beta\aket{j}_\alpha,\quad \varepsilon^{\alpha\beta}: \text{antisymmetric tensor}
    \end{gather*}
\end{frame}

\begin{frame}
    \frametitle{Modern Amplitude Method} 
 The answer is On-shell method.
    \begin{center}

% Text Node
\draw (233.4,128.25) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
% Text Node
\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
% Text Node
\draw (317.73,117.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.04,0.04}{On-shell method}}}}};
\end{tikzpicture}
\end{center}
\vspace{-1em}
    % 右侧：PT表达式
    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
    \begin{gather*}
        {A_5[1^+2^+3^+4^+5^+]=0}\\
        {A_5[1^-2^+3^+4^+5^+]=0}\\
        \textcolor{red}{A_5[1^-2^-3^+4^+5^+]=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trival one})\\
    \end{gather*}
    \vspace{-3em}
    \begin{gather*}
        {A_5[1^-2^-3^-4^-5^-]=0}\\
        {A_5[1^+2^-3^-4^-5^-]=0}\\
        \textcolor{red}{A_5[1^+2^+3^-4^-5^-]=\frac{[12]^4}{[12][23][34][45][51]}}
    \end{gather*}
\end{frame}

@@

\begin{frame}
    From Cauchy Theorem, we can ontain
    \begin{equation*}
        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
    \end{equation*}
    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
    \vspace{-1em}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.3\textwidth]{CT.png}
    \end{figure}
    \vspace{-1.5em}
    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
    \begin{equation*}
        \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
    This makes it easy to evaluate the residue at $z=z_I$
    \begin{equation*}
        -\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
\end{frame}

@@

\begin{frame}
    \frametitle{SQCD like sector}
    The amplitudes can be computed like 
    \begin{itemize}
        \item $\Phi^\dagger V_1V_1\Phi$
        \begin{align*}
            A[1^\Phi2^{\Phi^\dagger}3^+4^-]=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}\quad (\textcolor{red}{\text{Parke -Talyor like Formula}})
        \end{align*}
        \item $\Phi^\dagger V_1V_1V_1\Phi$
            \begin{equation*}
                A[1^\Phi2^{\Phi^\dagger}3^+4^+5^-]=\frac{\avg{15}^2\!\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
            \end{equation*}
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Pure 2-site amplitude}
    \begin{itemize}
        \item $\Phi V_2 \Phi^\dagger V_1$
        \begin{equation*}
            A[1^\Phi2^{\Phi^\dagger}3_1^+4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
        \end{equation*}
        \item $\Phi V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1^\Phi2^{\Phi^\dagger}3_1^+4_1^+5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
        \end{equation*}
        \item $\Phi V_2V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1^\Phi2^{\Phi^\dagger}3_1^+4_1^+5_2^+6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
        \end{equation*}       
    \end{itemize}
\end{frame}

@@

        \textcolor{red}{The equivalence between two different shift is related to powerful residue theorem (N. Arkani-Hamed, F. Cachazo, C. Cheung, and J. Kaplan,
        JHEP 1003, 020 (2010) [arXiv:0907.5418 [hep-th]].) and Grassmannian.}
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{CSW(Cachazo-Svrcek-Witten) expansion}
    We can also consider a shift that is implemented via a “holomorphic” square-spinor shift:
    \begin{equation*}
        \sket{\hat{i}}=\sket{i}+zc_i\sket{X},\qquad \aket{\hat{i}}=\aket{i}
    \end{equation*}
    Here $\sket{X}$ is an arbitrary reference spinor and the coefficients $c_i$ satisfy $\sum_{i=1}^{n} c_i \aket{i} = 0$.
    %Here we consider the situation where all $c_i\neq 0$, so that all momentum are shifted, called all-line shift.
    \begin{figure}
        \centering
        \includegraphics[width=0.7\textwidth]{NMHV.png}
    \end{figure}
    There are two possibilities: $\mathrm{anti\text{-}MHV_3}(=0)\times \mathrm{NMHV}$ ~or~ $\mathrm{MHV}\times\mathrm{MHV}$.
\end{frame}

>>>>

    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
    \begin{align*}
    A_5[1^+2^+3^+4^+5^+] &= 0 
    \qquad (\!+,-:~\text{\hyperlink{helicity}{helicity};} \\
    A_5[1^-2^+3^+4^+5^+] &= 0 
    \qquad 1,2,\cdots,n:~\text{particle labels}) \\
    \end{align*}
    \vspace{-3em}
    \hypertarget{conv}{}
    \pause
    \begin{gather*}
        {A_5[1^-2^-3^-4^-5^-]=0}\\
        {A_5[1^+2^-3^-4^-5^-]=0}\\
        \textcolor{red}{A_5[1^+2^+3^-4^-5^-]=\frac{[12]^4}{[12][23][34][45][51]}}
    \end{gather*}
\end{frame}

\begin{frame}
    \frametitle{Color-ordering for Yang-Mills}
    Consider the Yang-Mills lagrangian
    \begin{equation*}
        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_{\mu\nu}F^{\mu\nu})
    \end{equation*}
    The 3 point and 4 point vertices include $\tilde{f}^{abc}$ and $\tilde{f}^{abe}\tilde{f}^{cde}+\text{perms}$.

    (With a different convention,$\textrm{Tr}[T^aT^b]=\delta^{ab}$ and $[T^a,T^b]=i\tilde{f}^{abc}T^c$)

    We have 
    \begin{equation*}
        c_s=\tilde{f}^{a_1a_2b}\tilde{f}^{ba_3a_4},\quad c_t=\tilde{f}^{a_4a_1b}\tilde{f}^{ba_2a_3},\quad c_u=\tilde{f}^{a_1a_3b}\tilde{f}^{ba_2a_4}
    \end{equation*}
    and the color factor can be rewritten by the trace of product of generators
    \begin{equation*}
        i\tilde{f}^{abc}=\mathrm{Tr}([T^a,T^b]T^c),
    \end{equation*}
    Moreover, in $SU(N)$, we have a Fierz identity
    \begin{equation}
        \sum_{a}T^a_{ij}T^a_{kl}=\delta_{il}\delta_{kj}-\frac{1}{N}\delta_{ij}\delta_{kl}.
    \end{equation}
\end{frame}

\begin{frame}
    This identity is easier understood as matrix form like 
    \begin{align*}
    \mathrm{Tr}\{T^aA\}\mathrm{Tr}\{T^aB\}=\mathrm{Tr}\{AB\}-\frac{1}{N}\mathrm{Tr}\{A\}\mathrm{Tr}\{B\},\\
    \mathrm{Tr}\{AT^aBT^a\}=\mathrm{Tr}\{A\}\mathrm{Tr}\{B\}-\frac{1}{N}\mathrm{Tr}\{AB\}.
    \end{align*}
    So, the 4 gluon s-channel gives us
    \begin{align*}
        \tilde{f}^{a_1a_2b}\tilde{f}^{ba_3a_4}=\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_3}T^{a_4})-\mathrm{Tr}(T^{a_2}T^{a_1}T^{a_3}T^{a_4})\\
        -\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_4}T^{a_3})+\mathrm{Tr}(T^{a_2}T^{a_1}T^{a_4}T^{a_3}).
    \end{align*}
    Therefore, the full 4-point amplitude can be rewritten like
    \begin{equation*}
        \mathcal{A}_{4,\text{tree}}=g^2(A_4[1234]\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_3}T^{a_4})+\text{perms of } (234) )
    \end{equation*}
    here the subamplitudes $A_4[1234],A_4[1243]$, etc. are called \textbf{color-ordered ampltitudes}. This concept can be easily generalized to tree-level n-point case
    \begin{equation*}
        \textcolor{red}{\mathcal{A}_{n,\text{tree}}=g^{n-2}\sum_{\sigma}A_n[1,\sigma(2,3\cdots n)]\mathrm{Tr}(T^{a_1}T^{\sigma(a_2\cdots}T^{a_n)})}
    \end{equation*}
\end{frame}

@@

\begin{frame}
    From Cauchy Theorem, we can ontain
    \begin{equation*}
        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
    \end{equation*}
    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
    \vspace{-1em}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.3\textwidth]{CT.png}
    \end{figure}
    \vspace{-1.5em}
    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
    \begin{equation*}
        \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
    This makes it easy to evaluate the residue at $z=z_I$
    \begin{equation*}
        -\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\frac{(z-z_I)z_I}{z(z-z_I)}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)|_{z=z_I}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
\end{frame}

\begin{frame}
    \frametitle{Large z behavior}
    In the BCFW formula, the boundary term $B_n$ affects a lot
    \begin{equation*}
        A_n=-\sum_{z_I}\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
    \end{equation*}
    In most applications. one assumes or much better, proves $B_n=0$. This is often justified by declaring a stronger condition
    \begin{equation*}
        \textcolor{red}{\hat{A}_n(z)\rightarrow 0 \quad \text{for} \quad z\rightarrow \infty} 
    \end{equation*}
    Here I show the large z behavior for gluon scattering 
    \begin{center}
        \begin{tabular}{lrc}
            \toprule
            $[i\, \textbackslash \, j\rangle $ & $+$ & $-$ \\
            \midrule
            $+$ & $1/z$ & $z^3$ \\
            $-$ & $1/z$ & $1/z$ \\
            \bottomrule
          \end{tabular}
    \end{center}
    proved by using background field expansion ~\textcolor{green}{(N.~Arkani-Hamed and J.~Kaplan,
%``On Tree Amplitudes in Gauge Theory and Gravity,''
[arXiv:0801.2385 [hep-th]].)}
\end{frame}

@@

\begin{frame}
    \frametitle{SQCD like sector}
    The color factor in this sector looks like
    \begin{equation*}
        (T^{a_1}T^{a_2}\cdots T^{a_n})_{ij}
    \end{equation*}
    so we we need to notice is just the order of gauge boson.

    The amplitudes can be computed like 
    \begin{itemize}
        \item $\Phi^\dagger V_1V_1\Phi$
        \begin{align*}
            A[1^\Phi2^{\Phi^\dagger}3^+4^-]=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}\quad (\textcolor{red}{\text{Parke -Talyor like Formula}})
        \end{align*}
        \item $\Phi^\dagger V_1V_1V_1\Phi$
            \begin{equation*}
                A[1^\Phi2^{\Phi^\dagger}3^+4^+5^-]=\frac{\avg{15}^2\!\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
            \end{equation*}
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Pure 2-site amplitude}
    The straightforward way to observe the color structure in this case  is double line notation as follows 
        \vspace{-0.8em}
    \begin{center}
        \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

        \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=0.8,xscale=0.8]

%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Straight Lines [id:da7604191870446242] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (100,100) -- (150,100) ;
%Straight Lines [id:da7895005569652712] 
\draw [color={rgb, 255:red, 0; green, 110; blue, 237 }  ,draw opacity=1 ]   (100,110) -- (190,110) ;
%Straight Lines [id:da19217218880843812] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (150,50) -- (150,100) ;
%Straight Lines [id:da7866299736623521] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (160,50) -- (160,100) ;
%Straight Lines [id:da5667542352395977] 
\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (190,110) -- (190,160) ;
%Straight Lines [id:da33701635654582174] 
\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (200,110) -- (200,160) ;
%Straight Lines [id:da7076492571881566] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (299,100) -- (389,100) ;
%Straight Lines [id:da3803886589182971] 
\draw [color={rgb, 255:red, 0; green, 113; blue, 255 }  ,draw opacity=1 ]   (200,110) -- (250,110) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (128,103.83) -- (120,100.45) -- (127.97,96.99) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (153.28,70.33) -- (150.12,78.42) -- (146.44,70.55) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (156.49,77.35) -- (160.07,69.44) -- (163.33,77.49) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (340,102.83) -- (332,99.45) -- (339.97,95.99) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (120.93,107.08) -- (128.98,110.35) -- (121.06,113.93) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (193.4,129.42) -- (190,137.42) -- (186.55,129.45) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (196.55,138.41) -- (200,130.44) -- (203.4,138.44) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (220.93,107.08) -- (228.98,110.35) -- (221.06,113.93) ;
%Straight Lines [id:da696489944746132] 
\draw [color={rgb, 255:red, 0; green, 113; blue, 255 }  ,draw opacity=1 ]   (300,110) -- (350,110) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (321,107) -- (329.05,110.27) -- (321.13,113.84) ;
%Straight Lines [id:da24340791537710427] 
\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (350,110) -- (350,160) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (353.4,129.42) -- (350,137.42) -- (346.55,129.45) ;
%Straight Lines [id:da7298898466192736] 
\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (360,110) -- (360,160) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (356.55,138.41) -- (360,130.44) -- (363.4,138.44) ;
%Straight Lines [id:da3460055698725] 
\draw [color={rgb, 255:red, 0; green, 110; blue, 237 }  ,draw opacity=1 ]   (360,110) -- (450,110) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (380.93,107.08) -- (388.98,110.35) -- (381.06,113.93) ;
%Straight Lines [id:da4507056480848969] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (389,50) -- (389,100) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (393.28,70.33) -- (390.12,78.42) -- (386.44,70.55) ;
%Straight Lines [id:da6544383915955476] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (399,50) -- (399,100) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (395.49,77.35) -- (399.07,69.44) -- (402.33,77.49) ;
%Straight Lines [id:da03624471669725382] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (399,100) -- (449,100) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (427,103.83) -- (419,100.45) -- (426.97,96.99) ;
%Straight Lines [id:da34280653261510274] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (160,100) -- (250,100) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (201,102.83) -- (193,99.45) -- (200.97,95.99) ;

% Text Node
\draw (255,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
% Text Node
\draw (81,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
% Text Node
\draw (165,46.4) node [anchor=north west][inner sep=0.75pt]    {$V_{1}$};
% Text Node
\draw (325,143.4) node [anchor=north west][inner sep=0.75pt]    {$V_{2}$};
% Text Node
\draw (407,47.4) node [anchor=north west][inner sep=0.75pt]    {$V_{1}$};
% Text Node
\draw (285,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
% Text Node
\draw (454,95) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
% Text Node
\draw (166,142.4) node [anchor=north west][inner sep=0.75pt]    {$V_{2}$};

        \end{tikzpicture}
    \end{center}
    \begin{itemize}
        \item $\Phi V_2 \Phi^\dagger V_1$
        \begin{equation*}
            A[1^\Phi2^{\Phi^\dagger}3_1^+4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
        \end{equation*}
        \item $\Phi V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1^\Phi2^{\Phi^\dagger}3_1^+4_1^+5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
        \end{equation*}  
    \end{itemize}
\end{frame}

@@

        \textcolor{red}{The equivalence between two different shift is related to powerful residue theorem} \textcolor{green}{(N. Arkani-Hamed, F. Cachazo, C. Cheung, and J. Kaplan, [arXiv:0907.5418 [hep-th]].)} \textcolor{red}{and Grassmannian.}
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{CSW(Cachazo-Svrcek-Witten) expansion}
    We can also consider a shift that is implemented via a “holomorphic” square-spinor shift:
    \begin{equation*}
        \sket{\hat{i}}=\sket{i}+zc_i\sket{X},\qquad \aket{\hat{i}}=\aket{i}
    \end{equation*}
    Here $\sket{X}$ is an arbitrary reference spinor and the coefficients $c_i$ satisfy $\sum_{i=1}^{n} c_i \aket{i} = 0$.
    %Here we consider the situation where all $c_i\neq 0$, so that all momentum are shifted, called all-line shift.
    \begin{figure}
        \centering
        \includegraphics[width=0.7\textwidth]{NMHV.png}
    \end{figure}
    There are two possibilities: $\mathrm{anti\text{-}MHV_3}(=0)\times \mathrm{NMHV}$ ~or~ $\mathrm{MHV}\times\mathrm{MHV}$.
\end{frame}
